\documentclass[10pt]{article}

\begin{document}
\section{...stuff...}
-order the plugins are started\\
-platform dependent stuff, calling convention\\

\section{Generic functions}
The following three functions will be present in all the plugin libraries,
 in order to be recognized as valid PS2E plugins. They will help
 the emulator to find a plugin capabilities.

\subsection{PS2EgetLibType}
\begin{quote}\texttt{unsigned int} PS2EgetLibType(\texttt{void});\end{quote}

\begin{description}
\item[PS2EgetLibType] returns the type of the plugin.
 In fact it indicates the APIs supported by the dynamic library.
 The returned value can be one of:
\begin{itemize}
\item PS2E\_LT\_GS   0x01
\item PS2E\_LT\_PAD  0x02
\item PS2E\_LT\_SPU2 0x04
\item PS2E\_LT\_CDVD 0x08
\item PS2E\_LT\_DEV9 0x10
\end{itemize}
Currently, these are the only plugin types supported. Note that the values
 can be ORed.
\end{description}



\subsection{PS2EgetLibVersion2}
\begin{quote}\texttt{unsigned int} PS2EgetLibVersion2(\texttt{unsigned int}
 type);\end{quote}

\begin{description}
\item[PS2EgetLibVersion2] returns a combination of version numbers.
Parameter \emph{type} is used to select the functions set for which
 the emulator requests version information. See \texttt{PS2EgetLibType}
 for the values of this parameter.

The 5 APIs and their corresponding specs have changed over time.
 In order to prevent crashes and incompatibilities, a spec version have
 been introduced as the highest 16 bits of the returned value.
\begin{itemize}
\item PS2E\_GS\_VERSION   0x0002
\item PS2E\_PAD\_VERSION  0x0002
\item PS2E\_SPU2\_VERSION 0x0002
\item PS2E\_CDVD\_VERSION 0x0003
\item PS2E\_DEV9\_VERSION 0x0001
\end{itemize}
Notice that when the specs do change \texttt{and} the compatibility is broken,
 this version number is increased. The emulator loading code will support
 only one version for a certain library type at a time. If the internal
 version and plugin API version does not match, the plugin
 will not be loaded nor used.

The low half of the returned value reflects the version of the plugin itself.
 A major.minor versioning scheme is used on the two bytes like this:
\begin{verbatim}
...//code
return (PS2E_CDVD_VERSION<<16) | (0<<8) | (67);	//version 0.67
\end{verbatim}
\end{description}



\subsection{PS2EgetLibName}
\begin{quote}\texttt{char*} PS2EgetLibName(\texttt{void});\end{quote}

\begin{description}
\item[PS2EgetLibName] returns a string that contains a short\footnote{
less then 30 chars in one line} name. The string is stored
 in the plugin and will be used to represent the plugin in a config dialog.
\end{description}





\section{CDVD functions}
This section describes the functions that corresponds to CDVD\footnote{short for CD/DVD}
API - type PS2E\_LT\_CDVD(0x08).
 These specs are for PS2E\_CDVD\_VERSION(0x0003).

\subsection{CDVDinit}
\begin{quote}\texttt{int} CDVDinit(\texttt{void});\end{quote}

\begin{description}
\item[CDVDinit] does the initialization of the CDVD interface.
 It is the first function called; so, it can be used to do all the
 init stuff such as reading saved configuration, one-time hardware init and
 preparing the internal structures, tables, etc\ldots
 If an error is found the function will return -1, otherwise 0.
\end{description}



\subsection{CDVDshutdown}
\begin{quote}\texttt{void} CDVDshutdown(\texttt{void});\end{quote}

\begin{description}
\item[CDVDshutdown] is called when the emulator is closed. Do now the freeing
 operations. DO NOT FORGET TO FREE the resources used. The OS will probably
 free the garbage left, but some pieces of hardware might need a
 ``deinitialization'' procedure in order to work next time the emulator
 is run. Imagine that the user will choose another plugin to run with
 next time instead of yours, do not cause troubles.
\end{description}



\subsection{CDVDopen}
\begin{quote}\texttt{int} CDVDopen(\texttt{void});\end{quote}

\begin{description}
\item[CDVDopen] is called when the emulation starts.
 It is recommended that functions called from now on (until
 \texttt{CDVDclose} is met) to spend few processing time. Avoid calling
 blocking functions and if you do, the user should be notified visualy.
 Report errors by return value and warrings using a log.
 If an error is found the function will return -1 and the emulation stops,
 otherwise 0.

Do not report errors using message boxes while the emu runs, the GS plugin
 might use a display mode that can cause troubles to windowing system
 in showing your message.
\end{description}



\subsection{CDVDclose}
\begin{quote}\texttt{void} CDVDclose(\texttt{void});\end{quote}

\begin{description}
\item[CDVDclose] is called when the emulation is stopped. Some of the
 resources that you aquired with \texttt{CDVDstart} have to be released now
 in order that other programs to use them. If you locked the CD/DVD tray,
 unlock it so the user can change the disc.
\end{description}



\subsection{CDVDreadTrack}
\begin{quote}\texttt{int} CDVDreadTrack(\texttt{unsigned int}
 lsn, \texttt{int} mode);\end{quote}

\begin{description}
\item[CDVDreadTrack] is the function that performs the read of \texttt{a}
 sector from the CD/DVD. Parameter \emph{lsn} specifies the absolute value
 of the sector number in linear addressing mode without \emph{lead-in}\footnote{i.e.\
without leading 150 sectors == 2 seconds}. Usualy, the plugin will read
 a full sector of 2352 bytes in its internal buffer.
 The second parameter tells what port of ...
\end{description}

\end{document}

